\documentclass{beamer}

\mode<presentation>
{
  \usetheme{default}      % or try Darmstadt, Madrid, Warsaw, ...
  \usecolortheme{default} % or try albatross, beaver, crane, ...
  \usefonttheme{default}  % or try serif, structurebold, ...
  \setbeamertemplate{navigation symbols}{}
  \setbeamertemplate{footline}[frame number]
  \setbeamertemplate{caption}[numbered]
} 

\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}

\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}

\title[Git for Economists]{Git and GitHub: A Guide for Economists}
\author{Frank Pinter}
\date{Spring 2019}

\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Outline}
  \tableofcontents
\end{frame}

\section*{Introduction}

\begin{frame}{Introduction}
\end{frame}

\section{The importance of version control}

\begin{frame}{Life without version control}
You're writing a paper and you have a regression.
\begin{itemize}
\item Advisor 1 tells you to include a certain covariate. You put in lots of work to get the data, clean it, merge it, change the specification, and re-run.
\item Advisor 2 tells you that covariate is dumb. You remove it.
\item Then Advisor 2 changes their mind.
\end{itemize}
What do you do?
\end{frame}

\begin{frame}{Life without version control}
Do you keep every specification you ever tried?
\begin{itemize}
\item The code too, or just the outputs?
\item What if you discover a coding error that affects many of your specifications?
\end{itemize}
\end{frame}


\begin{frame}{Version control 0.1: putting dates on code}
\end{frame}

\begin{frame}{Version control 0.2: Dropbox}
A Post It note spotted on a grad student's desk:
\begin{quote}
	Don't forget! At 10:18 am on November 17th, we changed the specification to add new variable.
\end{quote}
Don't live this way.
\end{frame}

\begin{frame}{Useful principles}
\begin{enumerate}
\item You're not going to remember why you did that.
\item Your coauthor can't read your mind.
\item Conserve cognitive effort.
\item ``Not one piece of commercial software you have on your PC, your phone, your tablet,
your car, or any other modern computing device was written with the `date and initial' method.'' (Gentzkow and Shapiro)
\end{enumerate}

\end{frame}

\section{Using version control}

\begin{frame}{What's Git?}
\end{frame}

\begin{frame}{What software can I use?}
\begin{itemize}
\item GitKraken
\item GitHub Desktop
\item command line, old-school
\item RStudio (for R projects)
\end{itemize}

\end{frame}

\section{Using Git by yourself}

\begin{frame}{Commits: logging your changes}
\end{frame}

\begin{frame}{Branches: trying things out}
\end{frame}

\begin{frame}{Local vs. remote repo}
Git doesn't require a remote repository.
\begin{itemize}
\item If you have restrictions on your code (for example, if you work with confidential health data) you can use Git entirely locally
\item But a remote repository helps you keep things backed up seamlessly
\end{itemize}

\end{frame}

\section{Using Git for collaboration}

\begin{frame}{Repos}
\end{frame}

\begin{frame}{What's GitHub?}
\end{frame}

\section*{Conclusion}


\end{document}
